GPU-Beschleunigung der Material Point Method

### 2018-12-06 mscthesis.tex
performance

Aiming to get shaders memory-bandwidth limited while minimizing the amount of needed accesses for any given workload is the top-priority for our shaders. Achieving memory-bandwidth limit is equal to bringing the VRAM SOL\% between 60\% < top SOL\% < 80\%. The metrics Read Active\%, Write Active\% and Long Scoreboard\% will simultaneously increase by following that aim.
\clearpage
\section{Implementation}\label{sec:implementation}
GL\_EXT\_TIMER + NVIDIA Nsight\\
\subsection{GPU memory layout}
\noindent\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[caption={AoS Layout},language={GLSL},style={GL}]
struct Particle {
  vec4 position;
  vec4 velocity;
} Particles[n];
\end{lstlisting}
\end{minipage}
\hfill\noindent\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[caption={SoA Layout},label={llst:soa},language={GLSL},style={GL}]
struct Container{
  vec4 positions[n];
  vec4 velocities[n];
} Particles;
\end{lstlisting}
\end{minipage}

>>>>

Aiming to get shaders memory-bandwidth limited while minimizing the amount of needed accesses for any given workload is the top-priority for our shaders. Achieving memory-bandwidth limit is equal to bringing the VRAM SOL\% between 60\% < top SOL\% < 80\%. The metrics Read Active\%, Write Active\% and Long Scoreboard\% will simultaneously increase by following that aim.
\clearpage
\section{Implementation}\label{sec:implementation}
The computing time $\Delta t_c$ of shaders is gained by OpenGL timer queries \cite{KHRONOS:TIMER_QUERY}. A small benchmarker takes care of queuing timer queries and resolving them a frame later. This is done to not stall the GPU pipeline waiting on those queries. At the end of testing data is gathered and statistical quantities are written into a log file.
\subsection{GPU memory layout}
\noindent\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[caption={AoS Layout},language={GLSL},style={GL}]
struct Particle {
  vec4 position;
  vec4 velocity;
} Particles[n];
\end{lstlisting}
\end{minipage}
\hfill\noindent\begin{minipage}{0.45\textwidth}
\begin{lstlisting}[caption={SoA Layout},label={llst:soa},language={GLSL},style={GL}]
struct Container{
  vec4 positions[n];
  vec4 velocities[n];
} Particles;
\end{lstlisting}
\end{minipage}
